### 2014-03-14 docs/paper.tex
Use the fteproxy name.

The other category of obfuscation contains transports that take the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it to the destination.
Format-transforming encryption~\cite{fte} encodes data into strings that match a given regular expression,
in order to match a firewall's whitelist or avoid matching a blacklist.

>>>>

The other category of obfuscation contains transports that take the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it to the destination.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
in order to match a firewall's whitelist or avoid matching a blacklist.
